---
title: "e&r_commdiv"
output: html_document
editor_options: 
  chunk_output_type: console
---

goal is to make site by species matrices to do some double checking in the E&R analysis--this approach is to make sure that I can double check rarefaction and do more rigorous diversity using vegan, phyloseq, etc. 

```{r}
#initialization
rm(list=ls())

#setwd
setwd("/Volumes/GoogleDrive/My Drive/microrapidevo/submission_prep/e&r_only/")

#packages
require(ggplot2)
require(dplyr)
require(vegan)
require(reshape)
require(picante)
require(tidyverse)
require(phyloseq)
require(ranacapa)
require(RColorBrewer)
require(ggsignif)
require(data.table)

```


first, convert the famid2.csv into site by species matrix to prep for phyloseq
only needs to be done once
```{r}
rm(list=ls())

#red in raw data
rawdat<- read.table("e&r_data/remofamid2.csv", sep=",", header=TRUE)

#remove low abundance (less than 100 reads) to match with previous analsysis 
raw.clean<- filter(rawdat, totalreads > 100)

#make the matrix by transposing into treatment by family i.e. site by species. keeps track of total reads
#FUN just averages, but beacuse each treatment just has one observation, it doesn't average anything
sitesp<- cast(raw.clean, treatment ~ family, value="totalreads", FUN=mean )

#in this sitesp conversion, what are zeros are initial given NAs
#so change NaN's to 0's
sitesp[is.na(sitesp)] <- 0 

#make data frame
sitesp.df<- as.data.frame(sitesp)

#make rownames into the first column 
row.names(sitesp.df)<- sitesp.df$treatment
#remove treatment as first column 
sitesp.df[1]<- NULL

#transpose for phyloseq
sitesp.otumat<- as.data.frame(t(as.matrix(sitesp.df)))

##########make sure to change the name of the file############
#write table to import into phyloseq if need to do more fiddling
#write.table(sitesp.otumat, file="e&r_data/burke_otumat.csv", sep=",")
#have to rename to create "otuids" and don't know how to do this in R
#so do it in excel and reimport

```


defining file names here. Change for each one to simplify during phyloseq import
```{r}
rm(list=ls())

oturead<- "e&r_data/hardy_otumat.csv"

taxread<- "e&r_data/hardy_tax.csv"

metaread<- "e&r_data/hardy_meta.csv"

```



in this chunk, work way through specific analysis 
```{r}
#import into phyloseq

#import otu matrix
otu_table<- read.csv(oturead, sep=",", row.names=1)
otu_table<- as.matrix(otu_table)
OTU<- otu_table(otu_table, taxa_are_rows = TRUE)

#import into phyloseq
taxonomy<- read.csv(taxread, sep=",", row.names=1)
taxonomy<- as.matrix(taxonomy)
TAX<- tax_table(taxonomy)

#metadata
metadata<- read.table(metaread, sep=",", row.names = 1, header = TRUE)
META<- sample_data(metadata)

#check OTU names are consistent across objects
taxa_names(TAX)
taxa_names(OTU)

#check sample names
sample_names(OTU)
sample_names(META)

#import into phyloseq object
physeq<- phyloseq(OTU, META, TAX)

#double check that the everything is named correctly
sample_names(physeq)
sample_variables(physeq)
tax_table(physeq)

#check summary of sample data to see how to deal with treatment vs treatment.1 for rest of code
summary(physeq@sam_data)

```


remake figures for diversity, rarefaction, etc. 
```{r}
#remove viridae from the taxonomy
physeq<- physeq %>%
  subset_taxa(Kingdom != "Virus") %>%

#histogram for library size 
df.sizes<- as.data.frame(sample_data(physeq))
df.sizes$LibrarySize<- sample_sums(physeq)

#plot histogram of library size 
libsizeplot<-
ggplot(data=df.sizes, aes(x=LibrarySize, fill=group)) + 
    geom_histogram(binwidth=100000, color="white") +
    theme_classic() + 
    scale_fill_manual(values=c("#636363", "#66c2a5")) + 
    scale_color_manual(values=c("#636363", "#66c2a5")) +
    xlab("Read counts") +
    ylab("Number of samples") + 
    theme(legend.position="none")

#ggsave(libsizeplot, file="depthhisto/hardy_full.pdf", height=3, width=4)


#check barplots 
#first glom by the taxonomy. then psmelt to keep sample info together
#then calculate per individual pool (i.e. treatment.1) and calculate relabund and filter 
physeq_fam<- physeq %>%
    tax_glom(taxrank="Family") %>%
    psmelt() %>%
    group_by(treatment.1) %>%
    mutate(total=sum(Abundance)) %>%
    group_by(Family) %>%
    mutate(relabund = Abundance/total) %>%
    filter(relabund > 0.01)

#palette to visualize individuals 
famabund = length(unique(physeq_fam$Family))
getPal = colorRampPalette(brewer.pal(8, "Set3"))

#visualize relativey abundance 
plotfam<-
ggplot(data=physeq_fam, aes(x=Sample, y=Abundance, fill=Family)) +   
    geom_bar(stat="identity", position="fill") + 
    theme_classic() + 
    theme(legend.position="right") + 
    xlab("") + 
    ylab("Relative abundance (> 1%)") + 
    scale_fill_manual(values = getPal(famabund)) +
    labs(fill="Bacteria")+ 
    theme(legend.position="right") + 
    guides(fill=guide_legend(ncol=2)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(fill = "Family")

#ggsave(plotfam, file="specabund_ind/hardy_full.tiff", height=4, width=6)

#save rareplot so that the calculation doesn't have to be done again 
rareplot<- ggrare(physeq, step=1000, color="group", label=NULL, se=TRUE, plot=TRUE) 

#gussy up the plot to my own liking
raresave<-
  rareplot +
  theme_classic() + 
  scale_color_manual(values = c("#636363", "#66c2a5")) + 
  scale_fill_manual(values = c("#636363", "#66c2a5")) +
  xlab("Sampling depth") + 
  ylab("Family richness") +
  theme(legend.position = "none")

#ggsave(raresave, file="rarefactioncurves/hardy_fullb.pdf", height=3, width=4)

#remove wolbachia from this analysis
nowolb<- physeq %>%
  subset_taxa(Family != "Anaplasmataceae") %>%
  prune_taxa(taxa_sums(.) > 0, .)

nwdf.sizes<- as.data.frame(sample_data(nowolb))
nwdf.sizes$LibrarySize<- sample_sums(nowolb)

#plot histogram of library size 
nwlibsizeplot<-
ggplot(data=nwdf.sizes, aes(x=LibrarySize, fill=group)) + 
    geom_histogram(binwidth=10000, color="white") +
    theme_classic() + 
    scale_fill_manual(values=c("#636363", "#66c2a5")) + 
    scale_color_manual(values=c("#636363", "#66c2a5")) +
    xlab("Read counts") +
    ylab("Number of samples") + 
    theme(legend.position="none")

#ggsave(nwlibsizeplot, file="depthhisto/hardy_nw.pdf", height=3, width=4)


#barplots for individuals
nowolb_fam<- nowolb %>%
    tax_glom(taxrank="Family") %>%
    psmelt() %>%
    group_by(treatment.1) %>%
    mutate(total=sum(Abundance)) %>%
    group_by(Family) %>%
    mutate(relabund = Abundance/total) %>%
    filter(relabund > 0.01)

#palette to visualize individuals 
nwfamabund = length(unique(nowolb_fam$Family))
nwgetPal = colorRampPalette(brewer.pal(10, "Spectral"))

#scramble order for better visualization, but still nice colors
nwgetpal2<- sample(nwgetPal(nwfamabund))

#visualize relativey abundance 
plotnowolbfam<-
ggplot(data=nowolb_fam, aes(x=Sample, y=Abundance, fill=Family)) +   
    geom_bar(stat="identity", position="fill") + 
    theme_classic() + 
    theme(legend.position="right") + 
    xlab("") + 
    ylab("Relative abundance (> 1%)") + 
    scale_fill_manual(values = nwgetpal2) +
    labs(fill="Bacteria")+ 
    theme(legend.position="right") + 
    guides(fill=guide_legend(ncol=2)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(fill = "Family")

#ggsave(plotnowolbfam, file="specabund_ind/hardy_nw.tiff", height=4, width=6)


#look at rarefaction
rareplot.nw<-ggrare(nowolb, step=1000, color="group", label=NULL, se=TRUE, plot=TRUE)

rarenw.save<-
rareplot.nw +
  theme_classic() + 
  scale_color_manual(values = c("#636363", "#66c2a5")) + 
  scale_fill_manual(values = c("#636363", "#66c2a5")) +
  xlab("Sampling depth") + 
  ylab("Family richness") +
  theme(legend.position = "none")

#ggsave(rarenw.save, file="rarefactioncurves/hardy_nowolbb.pdf", height=3, width=4)

```

calculate alpha diversity in the samples, following denef lab suggestions. 
for the full bacterial community 
```{r}
#determine size to rarefy down to
minlib<- min(sample_sums(physeq))

#build df to store the trials. sampling diversity for 100 rarefactions for each sample 
nsamp = nsamples(physeq)
trials = 100

richness <- matrix(nrow = nsamp, ncol = trials)
row.names(richness) <- sample_names(physeq)

shannon <- matrix(nrow = nsamp, ncol = trials)
row.names(shannon) <- sample_names(physeq)

fisher <- matrix(nrow = nsamp, ncol = trials)
row.names(fisher) <- sample_names(physeq)

invsimp <- matrix(nrow = nsamp, ncol = trials)
row.names(invsimp) <- sample_names(physeq)

# It is always important to set a seed when you subsample so your result is replicable 
set.seed(3)

for (i in 1:100) {
  # Subsample
  r <- rarefy_even_depth(physeq, sample.size = minlib, verbose = FALSE, replace = FALSE)
  
  # Calculate measures
  rich <- as.numeric(as.matrix(estimate_richness(r, measures = "Observed")))
  richness[ ,i] <- rich
  
  shan <- as.numeric(as.matrix(estimate_richness(r, measures = "Shannon")))
  shannon[ ,i] <- shan
  
  fish<- as.numeric(as.matrix(estimate_richness(r, measures = "Fisher")))
  fisher[ ,i] <- fish
  
  invs<- as.numeric(as.matrix(estimate_richness(r, measures = "InvSimpson")))
  invsimp[ ,i] <- invs
}

#try to see if there's a weird problem with fisher only
estimate_richness(physeq, measures = "Shannon")

# Create a new dataframe to hold the means and standard deviations of richness estimates
SampleID <- row.names(richness)
mean <- apply(richness, 1, mean)
sd <- apply(richness, 1, sd)
measure <- rep("Richness", nsamp)
rich_stats <- data.frame(SampleID, mean, sd, measure)

# Create a new dataframe to hold the means and standard deviations of shannon estimates
SampleID <- row.names(shannon)
mean <- apply(shannon, 1, mean)
sd <- apply(shannon, 1, sd)
measure <- rep("Shannon", nsamp)
shann_stats <- data.frame(SampleID, mean, sd, measure)

SampleID <- row.names(fisher)
mean <- apply(fisher, 1, mean)
sd <- apply(fisher, 1, sd)
measure <- rep("Fisher", nsamp)
fish_stats <- data.frame(SampleID, mean, sd, measure)

SampleID <- row.names(invsimp)
mean <- apply(invsimp, 1, mean)
sd <- apply(invsimp, 1, sd)
measure <- rep("InvSimpson", nsamp)
invs_stats <- data.frame(SampleID, mean, sd, measure)

alpha <- rbind(rich_stats, shann_stats, fish_stats, invs_stats)

s <- data.frame(sample_data(physeq))
#quirk of dealing with phyloseq, but rename "treatment.1" to SampleID
names(s)[names(s) == "treatment.1"] <- "SampleID"
  
alphadiv <- merge(alpha, s, by = "SampleID") 

#order diversity facets
alphadiv$measure_f<- factor(alphadiv$measure, levels=c("Shannon", "InvSimpson", "Richness", "Fisher"))

#adding in variable to later facet to match individual graphs
alphadiv$status<- "Full bacterial community"

#visualize for whole community for wolbachia free experiment 
#divplot<- 
ggplot(alphadiv, aes(x=group, y=mean)) +
  facet_wrap(status~measure_f, scales = "free", ncol=4) +
  geom_boxplot() + 
  geom_point(aes(color=group)) + 
  scale_color_manual(values = c("#636363", "#66c2a5")) + 
  theme_bw() + 
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank()) + 
  theme(legend.position = "none") + 
  xlab("") + 
  ylab("Diversity measure") +
  geom_signif(comparisons = list(c(c("control", "evolved" ))), 
              map_signif_level = TRUE, test = "t.test") 

#ggsave(divplot, file="divmeasures/hardy_totalb.pdf", height=5, width=8)


```

repeat diversity measures for wolbachia removed dataset
```{r}
#determine size to rarefy down to
nwminlib<- min(sample_sums(nowolb))

#build df to store the trials. sampling diversity for 100 rarefactions for each sample 
nsamp = nsamples(nowolb)
trials = 100

nwrichness <- matrix(nrow = nsamp, ncol = trials)
row.names(nwrichness) <- sample_names(nowolb)

nwshannon <- matrix(nrow = nsamp, ncol = trials)
row.names(nwshannon) <- sample_names(nowolb)

nwfisher <- matrix(nrow = nsamp, ncol = trials)
row.names(nwfisher) <- sample_names(nowolb)

nwinvsimp <- matrix(nrow = nsamp, ncol = trials)
row.names(nwinvsimp) <- sample_names(nowolb)

# It is always important to set a seed when you subsample so your result is replicable 
set.seed(3)

for (i in 1:100) {
  # Subsample
  r <- rarefy_even_depth(nowolb, sample.size = nwminlib, verbose = FALSE, replace = FALSE)
  
  # Calculate measures
  rich <- as.numeric(as.matrix(estimate_richness(r, measures = "Observed")))
  nwrichness[ ,i] <- rich
  
  shan <- as.numeric(as.matrix(estimate_richness(r, measures = "Shannon")))
  nwshannon[ ,i] <- shan
  
  fish<- as.numeric(as.matrix(estimate_richness(r, measures = "Fisher")))
  nwfisher[ ,i] <- fish
  
  invs<- as.numeric(as.matrix(estimate_richness(r, measures = "InvSimpson")))
  nwinvsimp[ ,i] <- invs
}

# Create a new dataframe to hold the means and standard deviations of richness estimates
SampleID <- row.names(nwrichness)
mean <- apply(nwrichness, 1, mean)
sd <- apply(nwrichness, 1, sd)
measure <- rep("Richness", nsamp)
nwrich_stats <- data.frame(SampleID, mean, sd, measure)

# Create a new dataframe to hold the means and standard deviations of shannon estimates
SampleID <- row.names(nwshannon)
mean <- apply(nwshannon, 1, mean)
sd <- apply(nwshannon, 1, sd)
measure <- rep("Shannon", nsamp)
nwshann_stats <- data.frame(SampleID, mean, sd, measure)

SampleID <- row.names(nwfisher)
mean <- apply(nwfisher, 1, mean)
sd <- apply(fisher, 1, sd)
measure <- rep("Fisher", nsamp)
nwfish_stats <- data.frame(SampleID, mean, sd, measure)

SampleID <- row.names(nwinvsimp)
mean <- apply(nwinvsimp, 1, mean)
sd <- apply(nwinvsimp, 1, sd)
measure <- rep("InvSimpson", nsamp)
nwinvs_stats <- data.frame(SampleID, mean, sd, measure)

nwalpha <- rbind(nwrich_stats, nwshann_stats, nwfish_stats, nwinvs_stats)

nws <- data.frame(sample_data(nowolb))
#quirk of dealing with phyloseq, but rename "treatment.1.1" to SampleID
names(nws)[names(nws) == "treatment.1"] <- "SampleID"
  
nwalphadiv <- merge(nwalpha, nws, by = "SampleID") 

#order diversity facets
nwalphadiv$measure_f<- factor(nwalphadiv$measure, levels=c("Shannon", "InvSimpson", "Richness", "Fisher"))

#adding in variable to later facet to match individual graphs
nwalphadiv$status<- "Wolbachia removed"

```


make diversity measures figure
```{r}
#bind together both alphadiv and nwalphadiv
alphatotal<- rbind(alphadiv, nwalphadiv)

#plot
#totaldivplot<-
ggplot(alphatotal, aes(x=group, y=mean)) +
  facet_wrap(status~measure_f, scales = "free", ncol=4) +
  geom_boxplot() + 
  geom_point(aes(color=group)) + 
  scale_color_manual(values = c("#636363", "#66c2a5")) + 
  theme_bw() + 
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank()) + 
  theme(legend.position = "none") + 
  xlab("") + 
  ylab("Diversity measure") +
  geom_signif(comparisons = list(c("control", "evolved")), 
              map_signif_level = TRUE, test = "t.test")  

#ggsave(totaldivplot, file="divmeasures/hardy_totalb.pdf", height=10, width=8)

#write.table(alphatotal, file="e&r_data/hardy_diversity.csv", sep=",", row.names=FALSE)



```



to remake the main figure with this replicated sampling, need to save the withand without wolbachia. 
and then rebuild one big dataframe to recalculate all of this 
```{r}
#metadata for diversity (generations of selection)
genselect<- read.table("e&r_data/total_gentime.csv", sep=",", header=TRUE)

#need to bind together all of the diversity measures, saved from above
#read in all the files from data directory
div.file.names<- Sys.glob("e&r_data/*_diversity.csv")

#an empty dataframe to hold the data
divset<- data.frame()

#loop through and read each
for(i in 1:length(div.file.names)) {
  temp_data<- read.table(div.file.names[i], sep=",", header=TRUE)
  tempdf<- data.frame(temp_data)
  divset<- rbindlist(list(divset, tempdf))
}

#reorder factors
divset$study_f<- factor(divset$study, levels = c('accelerated development time', 
                                                 'delayed reproduction', 
                                                 'increased lifespan', 'egg size',
                                                 'desiccation resistance', 
                                                 'fluctuating temperature',
                                                 'salt and cadmium resistance', 
                                                 'starvation resistance', 
                                                 'parasitoid resistance', 'viral resistance'))

#for just full bacterial communities and Shannon, 
divset.full<- filter(divset, status =="Full bacterial community" & measure =="Shannon")

#write.table(divset.full, file="divsetfull.csv", sep=",", row.names=FALSE)

#plot diversity differences between control and evolved (Fig. 2)
#plot.divfull<-
ggplot(data=divset.full, aes(x=group, y=mean)) + 
  geom_boxplot() + 
  geom_point(aes(color=study_f)) +
  facet_wrap(study_f~., scales="free", nrow=2) + 
  scale_color_brewer(palette = "Spectral") + 
  theme_bw() + 
  theme(panel.grid=element_blank()) + 
  theme(legend.position = "none") +
  xlab("") + 
  ylab("Bacterial diversity (family)")
  
#ggsave(plot.divfull, file="figs_maintext/fig2_v2.png", width=11, height=6)

#calculate c diffs first
cdiffs<- divset.full %>%
  filter(group =="control") %>%
  group_by(study) %>%
  summarize(cmean = mean(mean))

#addback into divdiff df
divdiff<- divset.full %>%
  filter(group=="evolved") %>%
  #add back in length of selection. ignore the warning b/c it makes sense 
  left_join(genselect, by = c("study")) %>%
  #add back in cmean. ignore the warning b/c it makes sense
  left_join(cdiffs, by = c("study")) %>%
  #calculate diffs
  mutate(deltadiv = abs(mean-cmean)) %>%
  #log10 length of selection
  mutate(log10.length = log10(length.selection))

#plot for difference
#plot.deltadiff<-
ggplot(data=divdiff, aes(x=log10.length, y=deltadiv)) + 
  geom_point(aes(color=study_f)) + 
  scale_color_brewer(palette = "Spectral") +
  geom_smooth(method="lm") + 
  theme_classic() + 
  theme(legend.title = element_blank()) + 
  xlab("Duration of selection (log10)") + 
  ylab("Absolute change in diversity") + 
  theme(legend.position = "none") 

#ggsave(plot.deltadiff, file="figs_maintext/fig3_v2.png", height=4, width=4)

#stats check
div.m1<- lm(data=divdiff, deltadiv ~ log10.length)
#get p value
summary(div.m1)

#get r =0.30
cor(divdiff$log10.length, divdiff$deltadiv)

#compare with and without wolbachia plot
#to illustrate, use 4 different studies and look at Shannon diversity
wolb.divset<- divset %>%
  filter(measure == "Shannon") %>%
  filter(study == "accelerated development time" | study == "fluctuating temperature" |
         study == "starvation resistance" | study == "viral resistance")

#graph differences, faceted on +/- wolb
#plot.wolbcomp<-
ggplot(data=wolb.divset, aes(x=group, y=mean)) + 
  geom_boxplot() + 
  geom_point(aes(color=study_f)) + 
  facet_wrap(study_f~status, nrow = 2, scales="free") + 
  theme_bw() +
  xlab("") + 
  ylab("Bacterial diversity (family)") + 
  theme(legend.position = "none") + 
  theme(panel.grid = element_blank()) + 
  scale_color_manual(values=c("#9e0142", "#e6f598", "#66c2a5", "#5e4fa2"))

#ggsave(plot.wolbcomp, file="figs_maintext/fig4_v2.png", height=6.5, width=8.5)

```


stats for differences between control and evolved (summarized in Table 2)
```{r}
#convert the divset.full to data table  
divset.dt<- as.data.table(divset.full)

#t test across all treatments for the whole community 
ttest.full<- divset.dt[, t.test(data=.SD, mean~group), by=study]

#save ttest results from whole community 
#write.table(ttest.full, file="div_ttest_full.csv", sep=",", row.names=FALSE)

#filter for without wolbachia and only shannon diversity 
divset.nw<- filter(divset, status == "Wolbachia removed" & measure == "Shannon")

#convert to data table
divset.nw.dt<- as.data.table(divset.nw)

#t test across all treatments without wolbachia
ttest.nw<- divset.nw.dt[, t.test(data=.SD, mean~group), by=study_f]

#save ttest results 
#write.table(ttest.nw, file="div_ttest_nw.csv", sep=",", row.names=FALSE)

```






specific commands uniquefor each dataset
```{r}
#for burke, remove selected1 because very low abundance 
#subset_samples(treatment.1 != "selected1")

#for huang, anaplasmataceae actually is all lower than 100 reads. which is weird.
#factor adjust for this study 
#alphadiv$broad_f<- factor(alphadiv$broad, levels = c("control", "cadmium", "salt", "spatial", "temporal" ))


#for jha, with more than 1 group, use treatment and use broad instead of just control vs evolved



#for michalak data, there's some sort of problem trying to cast it into sitesp matrix
#Aggregation requires fun.aggregate: length used as default
#Error in mean.default(X[[i]], ...) : 'trim' must be numeric of length one

#i think its just unique to the michalak data. try another and copy into new file 
#there was a similar problem with orozco. 
#turns out there was duplication in the "treatment" category. I thought the "FUN=MEAN" would take care of it
#but had to go back and redo this and seemed to fix the problem. Or cast by srrid. both worked

#old way to calculate relative abundance. 
physeq_fam2<- physeq %>%
    tax_glom(taxrank="Family") %>%
    transform_sample_counts(function(x) {x/sum(x)}) %>%
    psmelt() %>%
    filter(Abundance > 0.01) %>%
    arrange(Family)

#saving files

#for wolbachia flies
#alphatotal$study<- studyname 
#write.table(alphatotal, file="e&r_data/burke_diversity.csv", sep=",")

#remove accelerated development (outlier in length)
divdiff.noacc<- filter(divdiff, study != "accelerated development time")

ggplot(data=divdiff.noacc, aes(x=log10.length, y=deltadiv)) + 
  geom_point(aes(color=study_f)) + 
  scale_color_brewer(palette = "Spectral") +
  geom_smooth(method="lm") + 
  theme_classic() + 
  theme(legend.title = element_blank()) + 
  xlab("Duration of selection (log10)") + 
  ylab("Absolute change in diversity") + 
  theme(legend.position = "none") 

div.m2<- lm(data=divdiff.noacc, deltadiv ~ length.selection+study_f )
hist(resid(div.m2))
shapiro.test(resid(div.m2))

#just double checking that the t test by data table worked
#filter for just one to see if it's a problem with ggsignif or the data table approach
div.accdev<- filter(divset.nw, study =="accelerated development time")
t.test(data=div.accdev, mean~group)
div.accdev<- filter(divset.full, study=="accelerated development time")
t.test(data=div.accdev, mean~group)

div.egg<- filter(divset.full, study=="egg size")
t.test(data=div.egg, mean~group)


#testing where the degrees of freedom gets stored (i think its parameter)
x <- rnorm(10)
y <- rnorm(10)
t.test(x,y)

test.tt<- t.test(x,y)


```

